---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gpsinterp

gpsinterp is an R package designed to interpolate gps-exif-tags (longitude, latitude
and directon), given a certain number of known points. The position of those exact points will be entered using JOSM (Java editor for OpenstreetMap).

It may be particularly useful for geolocating a sequence of photos (i.e. taken with small amount of time between each photo), typically a [mapillary](http://mapillary.com/app) sequence.

## Installation

You can install **gpsinterp** from github with :

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("the-knife/gpsinterp")
```
Note : _on Windows_, you need to have [RTools](https://cran.r-project.org/bin/windows/Rtools) to make devtools working.

## Other components to install

### _JOSM_ (required)

[JOSM](http://josm.openstreetmap.de) is an offline editor for OpenStreetMap. For this package, it is not used for uploading information to osm, but for locating exact points manually.

JOSM can display various aerial imageries and detect which points where moved by the user between two interpolations. *gpsinterp* will load local files in JOSM, therefore you have to enable the following options (in preferences menu) :

* "Enable remote control"
* "Open local files"

### _exiftool_ (optional)

[exiftool](http://sno.phy.queensu.ca/~phil/exiftool/) is a command line software for writing exif tags to photos. It only will be needed if you want to write computed information into
image files (other export type are possible).

On Linux, you can install exiftool with : ``sudo apt install libimage-exiftool-perl``

## Exporting results

### _csv file_

You can save latitude, longitude (and optionally direction) in a csv file.
Once the interpolation seems good enough, use the ``write_coord_csv`` function.

### _write exif in images_

If exiftool is installed on your system, you can write latitude, longitude (and optionally direction) into the images.
Once the interpolation seems good enough, use the ``write_exiftool`` function.

## Local directory architecture

You need to create two directories **input** and **output** on your machine.

* Put the orignal images in **input/photos**.

* Geolocated photos will be written in **output**.

## Typical iterative process for interpolation

```r
library(gpsinterp)

setwd("path/where/input/and/output/are")

# Initialize data
interp_init()

# Open JOSM.
# Create a new JOSM layer with at least two nodes and tagged with name="photo_xxx.JPG"
# (use the real names of the files)

# Save as "approx.osm" in the input directory

# Compute positions of missing points
interp_josm()

# 1/ Update some points in JOSM (don't forget to save)

# 2/ Compute new positions
interp_josm()
# (exact points will automatically be tagged as tourism=viepoint to distinguish them from interpolated ones)

# ....... Repeat 1/ and 2/ as many times as needed .......

# Save
write_exiftool()
  # or (if you don't have exiftool)
  write_coord_csv(file = "photos_coord.csv")

# Cleanup (optional, see help page)
interp_cleanup()
```
